SA on input prices
========================================================



```{r echo=FALSE}
library(ggplot2)
library(reshape2)

```


**assumptions:** correlated random draws on 'yield dependent' inputs of CAPRI and the NPK nutrient-prices
**method:** monte-carlo simulation, 1000 runs; using the GUSS solver option for CONOPT


Random draws
------------

Most volatile are fertilizer and fuel/energy prices.


```{r fig.width=7, fig.height=6}
load(file="n:/agpo/work1/himics/inputc/input_costs/draw_cov.RData")
# as the means are close to zero (remember they assumed to be normal with mean zero) we use the standard deviation instead of c.o.v.
p <- ggplot(subset(draw_cov, region=="DE000000"),aes(sd,reorder(input,sd)))
p + geom_point()
```


Induced variation in costs
--------------------------

Strangely poultry fattening has the highest coefficient of variation in most of the regions.

```{r fig.width=7, fig.height=6}
load(file="n:/agpo/work1/himics/inputc/input_costs/cost_cov.RData")
# ordered cov's in all regions
p <- ggplot(cost_cov, aes(cov,reorder(activity,cov)))
p+geom_point()
```

```{r fig.width=7, fig.height=6}
# ordered list of cov's in a selected region
p <- ggplot(subset(cost_cov, technology=="T" & region=="DE400000"),aes(cov,reorder(activity,cov)))
p + geom_point()
```


Induced changes in marginal gross value added
---------------------------------------------

Marginal Gross Value Added is used as a proxy for the income. The induced variation in MGVA varies across activities and regions. Residual activites like VSET or OFAR show big variation.

```{r fig.width=7, fig.height=6}
load(file="n:/agpo/work1/himics/inputc/input_costs/mgva_cov.RData")
# cov's for all regions
p <- ggplot(subset(mgva_cov, region!="DE000000"), aes(cov,reorder(activity,cov)))
p+geom_point()+xlim(0,0.3)
```

The aggregated figures for Germany: 
```{r fig.width=7, fig.height=6}
p <- ggplot(subset(mgva_cov, region=="DE000000"), aes(cov,reorder(activity,cov)))
p+geom_point()
```

Selected results
----------------


Most activity levels show little variation; they are quite stable.
See e.g. boxplots of activity levels in a selected region. Apart from PIGF, the ranges are small.

```{r fig.width=20, fig.height=6}
load(file="n:/agpo/work1/himics/inputc/input_costs/actlev.RData")
qplot(activity, value, data=subset(actlev, region=="DE230000" & technology=="T"), geom="boxplot")
```


Comparison of Z-scores for wheat over the regions:
```{r fig.width=10, fig.height=6}
load(file="n:/agpo/work1/himics/inputc/input_costs/scaled_actlev.RData")
qplot(value, data=subset(scaled_actlev, region!="DE000000" & technology=="T" & activity=="SWHE"), geom="density", color=region)
```


Comparison of Z-scores for different activities in a selected region:
```{r fig.width=10, fig.height=6}
qplot(value, data=subset(scaled_actlev, region=="DE230000" & technology=="T"), geom="density", color=activity)
```


An example box plot for SWHE in a selected region.
```{r fig.width=7, fig.height=6}
qplot(activity, value, data=subset(actlev, region=="DE230000" & technology=="T" & activity=="SWHE"), geom="boxplot")
```


The distribution of activity levels is usually flatter for T1 technology, see e.g. soft wheat in region DE230000
```{r fig.width=7, fig.height=6}
qplot(value, data=subset(actlev, region=="DE230000" & technology!="T" & activity=="SWHE"), geom="density", color=technology)
```

Ordered list of cov's per activities in a selected region. They are generally small...
```{r fig.width=7, fig.height=6}
load(file="n:/agpo/work1/himics/inputc/input_costs/levl_cov.RData")
p <- ggplot(subset(levl_cov, technology=="T" & region=="DE400000"),aes(cov,reorder(activity,cov)))
p + geom_point()
```

